### 2017-01-16 papers.tex
Adds new paper

>>>>

% =============================================================================
\section{\texttt{IND\_010} - Using Educational Data Mining Methods to Study the
Impact of Virtual Classroom in E-Learning}

Paper is~\cite{ind_010}. I haven't seen this paper has a reference of the
previous ones. But found it on Google Scholar while searching for Moodle Data
Mining. The techniques used in this paper are similar to~\cite{ind_008,
ind_003}.

The paper starts by talking about difficulties in e-learning environments. Such
as students feeling lonely and unsupported. They also talk about how web logs
need to be mined so meaningful information is taken from them.

This study is done to web logs. They have 824 students in 11 courses, but claim
that the number is superior. The study is done only to students who are remote.
They say that other studies such as 8, 13, and 14 e-learning platforms was used
to facilitate teacher-student interactions.

They start by preprocessing a group of features of students. Then they do
feature ranking using a few algorithms and build a decision tree based on the
Gain Ratio metric.

The decision tree predicts students grades based on their features.

This paper is another~\gls{dm} analysis made to Moodle. Like in previous works,
such as~\cite{ind_008, ind_003}, this paper goes through the process of
pre-processing Moodle data from e-learning courses, applying~\gls{dm}
techniques, and interpreting the results. The objectives of this paper are to
predict student grades given their usage of Moodle in an e-learning
environment.

The origins of the data are shown to come from 824 students in 11 courses. The
features of the data come from logs which say when a student logged in, when it
asked a question, and so on. The data mining process consists on applying a few
feature selection algorithms, such as gain ratio, $ \chi^2 $, SVN, and others,
to rank the features. In the end, a decision tree is built from the ranking
using gain ratio.

The built tree is able to predict the grades of a student given their features.
The first two levels of a built tree are shown and some interpretation is
given. For example, assertions are made about students that participate less
then 11 times in virtual classrooms which will probably fail the exams.

Although the results are presented and seem logical, the probabilities given
for each assertion of the decision tree are made so with small probabilities.
The previous example, for instance, only has 55\% probability. Some ways to
evaluate the accuracy of the built tree should be taken.

The methods listed in this paper are well explained and the results are clear.
Building decisions trees to predict students grades is a sound objective and a
common one in~\gls{edm}. The only negative points are the fact that the built
tree is not evaluated.

This paper is very relevant because it displays similar techniques
to~\cite{ind_008, ind_003}. The techniques for pre-processing and mining, the
datasets, and the conclusions are all very similar and will doubtless be very
important as a reference in future work.

References 18, 16, 5, 8, are 9 worth looking into.
